---
title: "generated exmple data for our package"
author: "Yunwei Zhang"
date: “`r paste0('Initiated on 20210607, compiled on ', format(Sys.time(), '%Y %b %d'))`”
output:
  
  html_document:
    code_folding: hide
    fig_height: 8
    fig_width: 12
    highlight: tango
    number_sections: yes
    theme: cosmo
    toc: yes
    toc_depth: 4
    toc_float:
      collapsed: yes
      smooth_scroll: no
  pdf_document:
    toc: yes
    toc_depth: '4'
    number_sections: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = FALSE,message = FALSE)
```

```{r}
library(KidneyAllocation)
library(dplyr)
library(gridExtra)
library(reshape2)
library(ggplot2)
library(ggpubr)
library(ggthemes)
library(survival)
library(pec)
library(ggridges)
library(plyr)
library(foreach)
library(doParallel)
library(doSNOW)
library(DT)
library(kableExtra)


```

# summary 
  
## Step1:   
  
  * for variables listed below, we randomly shuffle the values using seed 202106001
    
```
  "donor_height"    "recip_sex"    "recip_height"    "recip_weight" "donor_age"     "donor_sex"  "recip_age" "donor_weight" 
```
  * for variables listed below, we randomly shuffle the values using seed 202106002  
  
```
[1] "recip_graftno"       "donor_source"        "donor_state"         "recip_pra"           "donor_blgroup"      
[6] "donor_a1"            "donor_a2"            "donor_b1"            "donor_b2"            "donor_dr1"          
[11] "donor_dr2"           "donor_dq1"           "donor_dq2"           "recip_blgroup"       "recip_a1"           
[16] "recip_a2"            "recip_b1"            "recip_b2"            "recip_dr1"           "recip_dr2"          
[21] "recip_dq1"           "recip_dq2"   
```
  
  * for variables listed below, we randomly shuffle the values using seed 202106003
    
```
"donor_eth_code"     "donor_eth_country"   "donor_eth"           "donor_diabetes"      "donor_hypertension"  "donor_smoker"   "donor_death"         "donor_dcd"           "donor_creatinine"    "recip_state_initial" "recip_state_current""recip_age_rrtstart"  
```
  
  * for variables listed below, we randomly shuffle the values using seed 202106004
    
```
"recip_eth_detailed"  "recip_eth"           "recip_primrenal"    "recip_biopsy"        "recip_creatinine"         "recip_smoker"       "recip_state"   
```
  
  * for variables listed below, we randomly shuffle the values using seed 202106005

```
"tx_ischemia"   "tx_status"           "tx_period"           "tx_lstatus"          "tx_lperiod"          "tx_misa"            
"tx_misb"             "tx_misdr"            "tx_gfailcat"         "recip_waittime"      "recip_lung" 
```
  
  * for variables listed below, we randomly shuffle the values using seed 202106006

```
[61] "recip_coronary"      "recip_pvd"           "recip_cvd"           "recip_diabetes"      "recip_cancer"       
[66] "tx_organ"            "recip_waitstatus"    "recip_listtime"      "recip_epts"          "donor_kdri"         
[71] "algorithm"  
```
## Step2: 
  
* Assign new "recip_id", "tx_id" , "donor_id", where recip_id is one random letter with 6 random numbers, donor_id is two random letters with 6 random numbers, tx_id is three random letters with 6 random numbers
* For example, recip_id="P243279", donor_id="WH325126",tx_id="AYZ155939"

## Step3: 
  
  * sample new dates, for dates variables listed below
  
```
"tx_date","recip_rrtstartdate" , "recip_deathdate","tx_faildate", "recip_comorb_date", "recip_liststartdate"
```
 We sample another date value within two weeks before or after the real date using seed 202106001

# Step1: 

random sample all variabels (in rows), except date: "tx_date","recip_rrtstartdate" , "recip_deathdate","tx_faildate", "recip_comorb_date", "recip_liststartdate"

* notice here, the recipient age,weight,height are grouped and then sampled together, also, the donor age,weight,height
```{r}
rawdata=load("/Users/yzha0247/Documents/pkg/data/rawdata.rda")
set.seed(202106001)
order_index1=sample(nrow(rawdata))
set.seed(202106002)
order_index2=sample(nrow(rawdata))
set.seed(202106003)
order_index3=sample(nrow(rawdata))
set.seed(202106004)
order_index4=sample(nrow(rawdata))
set.seed(202106005)
order_index5=sample(nrow(rawdata))
set.seed(202106006)
order_index6=sample(nrow(rawdata))

selected_var=colnames(rawdata)[!colnames(rawdata)%in% c("tx_date","recip_rrtstartdate" , "recip_deathdate","tx_faildate", "recip_comorb_date", "recip_liststartdate","recip_id", "tx_id" , "donor_id")]

# * need to group recip age and gender and weight and height
# * need to group donor age and gender and weight and height
fakedata_part1=rawdata[order_index1,selected_var[c(23,24,37,43,44,47,48,50)]]
fakedata_part2=rawdata[order_index1,selected_var[1:22]]
fakedata_part3=rawdata[order_index1,selected_var[25:36]]
fakedata_part4=rawdata[order_index1,selected_var[c(38:42,45,46)]]
fakedata_part5=rawdata[order_index1,selected_var[c(49,51:60)]]
fakedata_part6=rawdata[order_index1,selected_var[61:71]]
fakedata_1=cbind.data.frame(fakedata_part1,fakedata_part2,fakedata_part3,fakedata_part4,fakedata_part5,fakedata_part6)


# fakedata_part1=rawdata[order_index1,selected_var[1:10]]
# fakedata_part2=rawdata[order_index1,selected_var[11:20]]
# fakedata_part3=rawdata[order_index1,selected_var[21:30]]
# fakedata_part4=rawdata[order_index1,selected_var[31:40]]
# fakedata_part5=rawdata[order_index1,selected_var[41:55]]
# fakedata_part6=rawdata[order_index1,selected_var[56:71]]
# fakedata_1=cbind.data.frame(fakedata_part1,fakedata_part2,fakedata_part3,fakedata_part4,fakedata_part5,fakedata_part6)
```

# Step2: 

assign new "recip_id", "tx_id" , "donor_id", where recip_id is one random letter with 6 random numbers, donor_id is two random letters with 6 random numbers, tx_id is three random letters with 6 random numbers
```{r}
idmaker <- function(x){
    max.val = x*100
    count <- nchar(as.character(max.val))                       # find out how many 'numbers' each ID will have after the letter
    size <- paste("%0",count,"d",sep="")                        # set the variable to be fed into 'sprintf' to ensure we have leading 0's
    lets <- toupper(sample(letters,x, replace=T))               # randomising the letters 
    nums <- sprintf(size,sample(1:max.val)[1:x])                # randominsing the numbers, and ensuing they all have the same number of characters
    ids <- paste(lets,nums,sep="")                              # joining them together
  return(ids)}

idmaker2 <- function(x){
    max.val = x*100
    count <- nchar(as.character(max.val))                       # find out how many 'numbers' each ID will have after the letter
    size <- paste("%0",count,"d",sep="")                        # set the variable to be fed into 'sprintf' to ensure we have leading 0's
    lets <- toupper(sample(letters,x, replace=T))  
    lets2 <- toupper(sample(letters,x, replace=T))# randomising the letters 
    nums <- sprintf(size,sample(1:max.val)[1:x])                # randominsing the numbers, and ensuing they all have the same number of characters
    ids <- paste(lets,paste(lets2,nums,sep=""),sep="")                              # joining them together
  return(ids)}

idmaker3 <- function(x){
    max.val = x*100
    count <- nchar(as.character(max.val))                       # find out how many 'numbers' each ID will have after the letter
    size <- paste("%0",count,"d",sep="")                        # set the variable to be fed into 'sprintf' to ensure we have leading 0's
    lets <- toupper(sample(letters,x, replace=T))    
    lets2 <- toupper(sample(letters,x, replace=T)) 
    lets3 <- toupper(sample(letters,x, replace=T)) # randomising the letters 
    nums <- sprintf(size,sample(1:max.val)[1:x])                # randominsing the numbers, and ensuing they all have the same number of characters
    ids <- paste(lets,paste(lets2,paste(lets3,nums,sep=""),sep=""),sep="")                             # joining them together
  return(ids)}
set.seed(202106001)
fakedata_1$recip_id=idmaker(dim(rawdata)[1])
fakedata_1$donor_id=idmaker2(dim(rawdata)[1])
fakedata_1$tx_id=idmaker3(dim(rawdata)[1])
fakedata_1$recip_id[1]
fakedata_1$donor_id[1]
fakedata_1$tx_id[1]
```


# Step3: 

sample new dates ("tx_date","recip_rrtstartdate" , "recip_deathdate","tx_faildate", "recip_comorb_date", "recip_liststartdate") using sliding windows,i.e.move before or after two weeks

```{r}
set.seed(202106001)
fakedata_1[,"tx_date"]=rawdata[,"tx_date"]+sample(-14:14,1)
fakedata_1[,"recip_rrtstartdate"]=rawdata[,"recip_rrtstartdate"]+sample(-14:14,1)
rawdata[,"recip_deathdate"]=as.Date(rawdata[,"recip_deathdate"],"%Y-%m-%d")
fakedata_1[,"recip_deathdate"]=rawdata[,"recip_deathdate"]+sample(-14:14,1)
fakedata_1[,"recip_liststartdate"]=rawdata[,"recip_liststartdate"]+sample(-14:14,1)
rawdata[,"tx_faildate"]=as.Date(rawdata[,"tx_faildate"],"%Y-%m-%d")
fakedata_1[,"tx_faildate"]=rawdata[,"tx_faildate"]+sample(-14:14,1)
fakedata_1[,"recip_comorb_date"]=rawdata[,"recip_comorb_date"]+sample(-14:14,1)

```

# data summary
```{r}
summary(fakedata_1)
kbl((summary(fakedata_1))) %>%
  kable_paper() %>%
  scroll_box(width = "1000px")
# datatable(fakedata_1,selection = "single", extensions = 'Buttons', options = list(
#       pageLength = 10,
#       lengthMenu = list(c(10, 50, -1), c('10', '50', 'All')),
#       dom = 'lfrBtip',
#       buttons = 
#         list(
#           buttons = c('csv', 'excel', 'pdf'),
#           text = 'Download'
#         )), caption = ("Example data"))
```


# check the package

```{r eval=FALSE}
rawdata=fakedata_1
save(rawdata,file="rawdata.rda")
#get raw_recip_matrix from rawdata
raw_recip_matrix <- fakedata_1[, grep("recip_", colnames(fakedata_1))]
raw_donor_matrix <- fakedata_1[, grep("donor_", colnames(fakedata_1))]
risk <- readRDS("predrisk_yw2.rds")
colnames(risk) <- c("recip_id", "riskscore")
raw_recip_matrix <- merge(raw_recip_matrix, risk, by= "recip_id", all.x=TRUE)
raw_donor_matrix$tx_date <- fakedata_1$tx_date
raw_recip_matrix$recip_algorithm <- fakedata_1$algorithm 
raw_recip_matrix$recip_id_original <- raw_recip_matrix$recip_id
raw_recip_matrix$recip_id <- paste(raw_recip_matrix$recip_id,
                                   raw_recip_matrix$recip_graftno,
                                   sep = "_")
raw_donor_matrix$donor_id <- as.character(raw_donor_matrix$donor_id)
raw_donor_matrix$donor_blgroup <- as.character(raw_donor_matrix$donor_blgroup)
raw_recip_matrix$recip_blgroup <- as.character(raw_recip_matrix$recip_blgroup)
raw_recip_matrix$recip_id <- as.character(raw_recip_matrix$recip_id)
raw_donor_matrix <- raw_donor_matrix %>% group_by(donor_id) %>% dplyr::mutate(num_kidney = n()) %>%distinct(donor_id, .keep_all = TRUE) 
raw_recip_matrix <- data.frame(raw_recip_matrix)
raw_donor_matrix <- data.frame(raw_donor_matrix)
raw_recip_matrix$recip_original_listdate <- raw_recip_matrix$recip_liststartdate
raw_recip_matrix$recip_original_rrtstartdate<- raw_recip_matrix$recip_rrtstartdate
raw_donor_matrix <- raw_donor_matrix[raw_donor_matrix$tx_date > "2008-09-18",]
dim(raw_recip_matrix)
dim(raw_donor_matrix)
raw_recip_matrix$recip_tx_date <- fakedata_1$tx_date
raw_recip_matrix$recip_birthdate <- raw_recip_matrix$recip_tx_date - lubridate::years(raw_recip_matrix$recip_age)
summary(raw_recip_matrix$recip_birthdate)
raw_recip_matrix <- raw_recip_matrix %>% tidyr::drop_na(recip_epts, recip_state, recip_birthdate, recip_age, recip_pra)
raw_donor_matrix <- raw_donor_matrix %>% tidyr::drop_na(donor_kdri, donor_state, donor_age)
keep <- raw_recip_matrix$recip_rrtstartdate < raw_recip_matrix$recip_liststartdate
raw_recip_matrix <- raw_recip_matrix[keep, ]
dim(raw_recip_matrix)
########added 20210504 by Yunwei
keep2 <- raw_recip_matrix$recip_tx_date>raw_recip_matrix$recip_liststartdate
raw_recip_matrix <- raw_recip_matrix[keep2, ]
dim(raw_recip_matrix)
######## changed from 5821 to 5776
dim(raw_donor_matrix)


hla_data <- fakedata_1 %>% dplyr::select(recip_id, tx_misa, tx_misb, tx_misdr, donor_state)
raw_recip_matrix<-merge(raw_recip_matrix, hla_data, by.x = "recip_id_original", by.y = "recip_id", all.x=TRUE) %>% dplyr::rename("recip_tx_misa" ="tx_misa",
                                                                                            "recip_tx_misb" = "tx_misb",
                                                                                            "recip_tx_misdr" = "tx_misdr",
                                                                                            "origin_donor_state" = "donor_state")

raw_recip_matrix<- raw_recip_matrix[!duplicated(raw_recip_matrix$recip_id_original),]
dim(raw_recip_matrix)

```



```{r eval=FALSE}
pra_group <- cut(fakedata_1$recip_pra,
                 c(0, 20, 40, 60, 80, 100),
                 include.lowest = TRUE,
                 right = FALSE)
pra_group_prob <- c(0.84, 0.05, 0.03, 0.02, 0.05) #changed this 20210423
names(pra_group_prob) <- levels(pra_group)
blood_group_prob <- c(0.3, 0.02, 0.17, 0.51)
names(blood_group_prob) <- c("A", "AB", "B", "O")
state_prob <- round(c(531, 340, 106, 56, 42)/1075, 2)
names(state_prob) <- c("NSW", "VIC", "QLD", "SA", "WA")
grid_prob <- expand.grid(pra_group_prob, blood_group_prob, state_prob)
grid_prob <- grid_prob[, 1] * grid_prob[, 2] * grid_prob[, 3]
grid_prob <- cbind(expand.grid(names(pra_group_prob), 
                               names(blood_group_prob),
                               names(state_prob)),
                   prob = grid_prob)

##############added by yunwei, not sure why this doesnt exist
raw_recip_matrix$pra_group <- cut(raw_recip_matrix$recip_pra,
                 c(0, 20, 40, 60, 80, 100),
                 include.lowest = TRUE,
                 right = FALSE)

multiple_sampling_recip_matrix_fun=function(seed){
num_recip_size = 1500
set.seed(seed)
grid_prob$num <- round(grid_prob$prob * num_recip_size)
grid_prob$Var3 <- as.character(grid_prob$Var3)
raw_recip_matrix_subset <- c()
for (i in 1:nrow(grid_prob)) {
  tmp <- raw_recip_matrix %>% filter(recip_blgroup == grid_prob[i, 2],pra_group == grid_prob[i, 1],recip_state == grid_prob[i, 3])
  num_tmp <- min(grid_prob[i, 5], nrow(tmp))
  tmp <- tmp[sample(1:nrow(tmp), size = num_tmp), ]
  raw_recip_matrix_subset <- rbind(raw_recip_matrix_subset, tmp)
}

round(table(raw_recip_matrix_subset$recip_state)/length(raw_recip_matrix_subset$recip_state), 2)

round(table(raw_recip_matrix_subset$recip_blgroup)/length(raw_recip_matrix_subset$recip_blgroup), 2)
raw_recip_matrix_subset$pra_group <- cut(raw_recip_matrix_subset$recip_pra,
                                         c(0, 20, 40, 60, 80, 100),
                                         include.lowest = TRUE,
                                         right = FALSE)
round(table(raw_recip_matrix_subset$pra_group)/length(raw_recip_matrix_subset$pra_group), 2)
round(table(raw_recip_matrix_subset$recip_age_group)/nrow(raw_recip_matrix_subset), 2)
round(table(raw_recip_matrix_subset$recip_state)/nrow(raw_recip_matrix_subset), 2)
return(raw_recip_matrix_subset)
}


raw_recip_matrix_subset=multiple_sampling_recip_matrix_fun(1)

which(!colnames(raw_donor_matrix) %in% c("donor_source","donor_state","donor_blgroup",
                                            "donor_a1", "donor_a2","donor_b1","donor_b2"
                                            ,"donor_dr1" ,"donor_dr2"
                                             ,"donor_dq1" ,"donor_dq2","donor_height"
                                             ,"donor_weight","donor_eth_code" ,"donor_eth_country"
                                             ,"donor_eth"  ,"donor_diabetes", "donor_hypertension"
                                             ,"donor_smoker", "donor_id","donor_death"
                                             ,"donor_dcd"  ,"donor_creatinine" ,"donor_age"
                                             ,"donor_sex"  ,"donor_kdri", "tx_date"
                                             ,"num_kidney" ))


raw_recip_matrix_subset=raw_recip_matrix_subset[,-which(!colnames(raw_recip_matrix_subset) %in% c("recip_id" , "recip_graftno", "recip_pra"
                                           ,"recip_blgroup" ,"recip_a1","recip_a2"
                                           ,"recip_b1" , "recip_b2","recip_dr1"
                                           ,"recip_dr2", "recip_dq1","recip_dq2"
                                           ,"recip_state_initial","recip_state_current", "recip_age_rrtstart"
                                           , "recip_sex","recip_eth_detailed" ,"recip_eth"
                                           , "recip_primrenal", "recip_biopsy" , "recip_creatinine"
                                           ,"recip_height","recip_weight" ,"recip_smoker"
                                           ,"recip_rrtstartdate", "recip_deathdate", "recip_state"
                                           , "recip_age", "recip_waittime","recip_lung"
                                           ,"recip_coronary", "recip_pvd","recip_cvd"
                                           ,"recip_diabetes", "recip_comorb_date"  ,"recip_cancer"
                                           ,"recip_liststartdate", "recip_waitstatus", "recip_listtime"
                                           ,"recip_epts", "riskscore", "recip_algorithm"
                                           ,"recip_id_original", "recip_original_listdate" ,"recip_original_rrtstartdate"
                                           ,"recip_tx_date", "recip_birthdate" ,"pra_group"
                                           ,"recip_age_group"))]


#10 times 
recip_sample_list=list()
for(i in 1:10){
  recip_sample_list[[i]]=multiple_sampling_recip_matrix_fun(i)
}
saveRDS(recip_sample_list,"recip_sample_list.rds")
save(raw_recip_matrix_subset,raw_donor_matrix,raw_recip_matrix,file="newdata.rda")
```


```{r eval=FALSE}

result=KidneyAllocation::runSimulation5.4(raw_recip_matrix_subset, 
                                 raw_donor_matrix,
                                 algorithm_FUN = KidneyAllocation::allocation_national,
                                 eligible_FUN = KidneyAllocation::selectionpool1.2,
                                 matching_FUN = KidneyAllocation::dmNational_formula,
                                 waitlist_FUN = KidneyAllocation::dynamic_waitlist,
                                 state_algorithm = TRUE,
                                 national_algorithm_threshold = 54000000,
                                 state_algorithm_FUN = KidneyAllocation::Australia_state_algorithm,
                                 state_eligible_FUN = KidneyAllocation::Australia_state_selectionpool,
                                 state_matching_FUN = KidneyAllocation::dmState_formula,
                                 eligible_arg = list(AB_priority = TRUE),
                                 waitlist_arg = list(waitlist_Risk = FALSE),
                                 resampleN = 1,
                                 verbose = FALSE,
                                 num_donor = 800,num_recip = 300,
                                 state_balance = TRUE,
                                 dynamic_waitlist = TRUE, 
                                 National_II = TRUE,
                                 is_parallel=FALSE,
                                 ncores = 10)

length(result)
dim(result[[1]])
dim(result[[2]])
dim(result[[3]])
dim(result[[4]])
head(result[[1]])

```



















