---
title: "SimKAP--simulation of the kidney allocation process"
author:
- name: Yunwei Zhang 20210524
  affiliation: 
  - School of Mathematics and Statistics, The University of Sydney, Australia
  - Charles Perkins Centre, The University of Sydney, Australia
output: rmarkdown::html_vignette
code_folding: "hide"
vignette: >
  %\VignetteIndexEntry{KidneyAllocation}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---
  
  
```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    warning = FALSE,
    message = FALSE,
    comment = "#>"
)
```


# Introduction

`simKAP` is an R package to simulate the kidney alocation process to get realistic recipient-donor pairs take into consideration of **human intervention** and **dynamic waiting list modeling**.   
This vignette will walk through the implementation of this process using **Australia recipient waiting list**, **Australia transplantation data** and under **Australia kidney allocation algorithm**. With this demonstration using working exmaple, you will be able to customise your allocation process with modified functions such as a new National allocation (see section **Customisable allocation process**)

# Loading Packages and Data

First, load `simKAP` via install `KidneyAllocation`.

```{r eval = FALSE}
install.packages("KidneyAllocation")
```

Then, we load the example data sampled from Australia kidney allocation database.
```{r}
library(KidneyAllocation)
data("rawdata")
data("newdata")
recip_sample_list=readRDS("recip_sample_list.rds")
raw_donor_matrix$donor_rank = rank(raw_donor_matrix[,'donor_kdri']) / nrow(raw_donor_matrix)
```

Notice here, the features required from the historical transplant data are listed below:
```
donor_feature=c("donor_source","donor_state","donor_blgroup",
                                            "donor_a1", "donor_a2","donor_b1","donor_b2"
                                            ,"donor_dr1" ,"donor_dr2"
                                             ,"donor_dq1" ,"donor_dq2","donor_height"
                                             ,"donor_weight","donor_eth_code" ,"donor_eth_country"
                                             ,"donor_eth"  ,"donor_diabetes", "donor_hypertension"
                                             ,"donor_smoker", "donor_id","donor_death"
                                             ,"donor_dcd"  ,"donor_creatinine" ,"donor_age"
                                             ,"donor_sex"  ,"donor_kdri", "tx_date"
                                             ,"num_kidney" )
recipient_feature=c("recip_id" , "recip_graftno", "recip_pra"
                                           ,"recip_blgroup" ,"recip_a1","recip_a2"
                                           ,"recip_b1" , "recip_b2","recip_dr1"
                                           ,"recip_dr2", "recip_dq1","recip_dq2"
                                           ,"recip_state_initial","recip_state_current", "recip_age_rrtstart"
                                           , "recip_sex","recip_eth_detailed" ,"recip_eth"
                                           , "recip_primrenal", "recip_biopsy" , "recip_creatinine"
                                           ,"recip_height","recip_weight" ,"recip_smoker"
                                           ,"recip_rrtstartdate", "recip_deathdate", "recip_state"
                                           , "recip_age", "recip_waittime","recip_lung"
                                           ,"recip_coronary", "recip_pvd","recip_cvd"
                                           ,"recip_diabetes", "recip_comorb_date"  ,"recip_cancer"
                                           ,"recip_liststartdate", "recip_waitstatus", "recip_listtime"
                                           ,"recip_epts", "riskscore", "recip_algorithm"
                                           ,"recip_id_original", "recip_original_listdate" ,"recip_original_rrtstartdate"
                                           ,"recip_tx_date", "recip_birthdate" ,"pra_group"
                                           ,"recip_age_group")

tablee=cbind.data.frame(donor_feature,recipient_feature)
kbl(tablee) %>%
  kable_paper() %>%
  scroll_box(width = "100px")
```


Lastly, we load other packages for this vignette.
```{r}
library(dplyr)
library(gridExtra)
library(reshape2)
library(ggplot2)
library(ggpubr)
library(ggthemes)
library(survival)
library(pec)
library(ggridges)
library(plyr)
library(foreach)
library(doParallel)
library(doSNOW)
```

# Allocation process under **Australia kidney allocation algorithm**

The process is implemented through one huge function named `runSimulation5.4` which calls dependent functions inside itself. This below example shows how to use this function and details about each argument are illustrated.

```{r eval=FALSE}
# example allocation process
result=KidneyAllocation::run_simulation(recip_sample_list[[1]], 
                                 raw_donor_matrix,
                                 algorithm_FUN = KidneyAllocation::allocation_national,
                                 eligible_FUN = KidneyAllocation::selection_default,
                                 matching_FUN = KidneyAllocation::dm_national_formula,
                                 waitlist_FUN = KidneyAllocation::dynamic_waitlist,
                                 state_algorithm = TRUE,
                                 national_algorithm_threshold = 54000000,
                                 state_algorithm_FUN = KidneyAllocation::australia_state_algorithm,
                                 state_eligible_FUN = KidneyAllocation::australia_state_selection,
                                 state_matching_FUN = KidneyAllocation::dm_state_formula,
                                 eligible_arg = list(AB_priority = TRUE),
                                 waitlist_arg = list(waitlist_Risk = FALSE),
                                 resampleN = 1,
                                 verbose = FALSE,
                                 num_donor = 800,num_recip = 300,
                                 state_balance = TRUE,
                                 dynamic_waitlist = TRUE, 
                                 National_II = TRUE,
                                 is_parallel=FALSE,
                                 ncores = 10)
saveRDS(result,"simKAP_eval.rds")
```

1. `recip_sample_list` is a list of length 10 with 10 different samples contains recipient features, we take one sample from it to be used as our recipient matrix. 
```{r}
length(recip_sample_list)
head(recip_sample_list[[1]])
dim(recip_sample_list[[1]])
```

2. `raw_donor_matrix` is a donor matrix contains donor features
```{r}
head(raw_donor_matrix)
dim(raw_donor_matrix)
```

3. `algorithm_FUN` and `state_algorithm_FUN` implement the Australia national and state allocation algorithms, notice here if you have your own algorithm, you can change this to your function name. 

4. `eligible_FUN` gives options to customise the eligible recipient pool, which means if you want to have a different pool with further restriction on eligible recipients, you can change it here.

This gives us a `list` of length 4 as the output (notice that you can take our saved result to have a look) and based on this list, you can analyse and demonstrate with your own preference. 
  
  The first one is the matched recipients and donors dataset with all **recipient features**, **donor features** and **transplant matchability features**.
  The second one is all those disgarded donor kidneys with the associated donor kidney features.
  The third one contains all those different donor-recipient state kidneys, i.e. those kidneys to achieve state balance.
  The last one is the dynamic waiting list results (corresponding to each recipient in the first full dataset)
```{r}
simKAP_eval=readRDS("simKAP_eval.rds")
length(simKAP_eval)
dim(simKAP_eval[[1]])
dim(simKAP_eval[[2]])
dim(simKAP_eval[[3]])
dim(simKAP_eval[[4]])
```



# Customisable allocation process

This example simulation process shows the paried result under the `CORisk allocation algorithm` with a threshold number 0.2 introduced in our paper. 
Detailed main changes for this new algorithm compared with the above one are: `eligible_FUN`, `matching_FUN`, `state_matching_FUN`, `waitlist_FUN`. With no specification of `matching_FUN`, `state_matching_FUN`, `waitlist_FUN`, the dynamic waiting list and share decision making procedures are not implemented in this new algorithm. The threshold number is specified through the `eligible_arg` argument using `threshold_number=0.2`.

```{r eval=FALSE}
result_new=KidneyAllocation::run_simulation(recip_sample_list[[1]], 
                                   raw_donor_matrix,
                                   algorithm_FUN = allocation_national,
                                   eligible_FUN = selection_corisk,
                                   matching_FUN = select_max,
                                   state_algorithm = TRUE,
                                   national_algorithm_threshold = 54000000,
                                   state_algorithm_FUN = australia_state_algorithm,
                                   state_eligible_FUN = australia_state_selection,
                                   state_matching_FUN = select_max,
                                   eligible_arg = list(AB_priority = TRUE,threshold_number=0.2),
                                   resampleN = 1,
                                   verbose = FALSE,
                                   num_donor = 800,num_recip = 300,
                                   state_balance = TRUE,
                                   dynamic_waitlist = FALSE, 
                                   National_II = TRUE )
saveRDS(result_new,"us0.2full.rds")
```

This gives us a `list` of length 3 as the output (notice that you can take our saved result to have a look) and based on this list, you can analyse and demonstrate with your own preference. 
  
  The first one is the matched recipients and donors dataset with all **recipient features**, **donor features** and **transplant matchability features**.
  The second one is all those disgarded donor kidneys with the associated donor kidney features.
  The third one is 

```{r}
us0.2=readRDS("us0.2full.rds")
length(us0.2)
dim(us0.2[[1]])
dim(us0.2[[2]])
dim(us0.2[[3]])
```


# Session Info

```{r}
sessionInfo("KidneyAllocation")
```

